### 2015-05-13 corral.tex
update

\noindent
\textbf{Sound Partial-Order Reduction}\xspace\xspace By default, \corral instruments a \texttt{yield} statement (which denotes a potential nondeterministic context-switch) before each \emph{visible operation} (i.e., synchronization operations and shared memory accesses) of every thread. It then leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound.

@@

\noindent
\textbf{Race-Checking Instrumentation}\xspace\xspace In this paper, we treat races as bugs. To detect them, we employ a simple, but effective, encoding of data race checks within \corral.
For example, whenever there is a write access to a shared variable, such as
\texttt{\$M.13 := 0}, we instrument the Boogie IVL code to check for write-write
races as follows:
%
\begin{boogie}
$M.13 := 0;        // original write
yield;             // allow for a context-switch
assert $M.13 == 0; // check written value
\end{boogie}
%
Likewise, for a read access to a shared variable, such as \texttt{\$p0 :=
\$M.13}, we instrument the Boogie IVL code to check for read-write races as
follows:
%
\begin{boogie}
$p0 := $M.13;        // original read
yield;               // allow for a context-switch
assert $p0 == $M.13; // check read value
\end{boogie}

>>>>

\medskip\noindent\textbf{Sound Partial-Order Reduction }
%
By default, \corral instruments a \texttt{yield} statement (which denotes a potential nondeterministic context-switch) before each \emph{visible operation} (i.e., synchronization operations and shared memory accesses) of every thread. It then leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound.

@@

\medskip\noindent\textbf{Race-Checking Instrumentation }
%
In this paper, we treat races as bugs. To detect them, we employ a simple, but effective, encoding of data race checks within \corral. For example, whenever there is a write access to a shared variable $s$, we instrument our abstract Boogie program to check for write-write races as follows:
%
\begin{boogie}
s = e;         // original write
yield;         // allow for a context-switch
assert s == e; // check written value
\end{boogie}
%
Likewise, for a read access to a shared variable $s$, we instrument the abstract Boogie program to check for read-write races as follows:
%
\begin{boogie}
x = s;         // original read
yield;         // allow for a context-switch
assert x == s; // check read value
\end{boogie}
